Summary of the things that I learned

### 2024-10-26 300-univalent-foundations.tex
Improve another couple of citations
Improve one additional citation

\begin{lemma}
  For every category $ C $, there exists a univalent category $ D $ with a weak equivalence
  \[ \iota: C \hookrightarrow D. \]
\end{lemma}
\begin{proof}
  One construction takes $ D $ to be the full subcategory of the presheaf category $ PC $ of objects that are isomorphic (there \textit{merely exists} an isomorphism) to the Yoneda embedding $ \yo(X) $ of some object $ X : C $. See \autocite{univalent-categories}, Theorem 8.5.
\end{proof}
We call such a univalent category a \iindex{Rezk completion} of $ C $. Actually, we can call it \textit{the} Rezk completion:
\begin{lemma}[\coqident{Bicategories.RezkCompletions.Uniqueness}{rezk_completion_unique}]
  A Rezk completion is unique.
\end{lemma}
\begin{proof}
  Precomposition with the weak equivalence $ \iota: C \hookrightarrow D $ gives an adjoint equivalence on the functor categories $ [D, E] \simeq [C, E] $ for any univalent category $ E $. From this, it follows that $ \iota $ is the ``initial functor'' from $ C $: any functor from $ C $ to a univalent category factors uniquely through $ \iota $.

@@

Lastly, a result about univalent categories that we will use a couple of times in this thesis:
\begin{lemma}\label{lem:univalen-category-equivalence}
  For a functor between univalent categories $ F: A \to B $, the types `$ F $ is an adjoint equivalence' and `$ F $ is a weak equivalence' are equivalent propositions (see Section \ref{sec:homotopy-props-sets}).
\end{lemma}
\begin{proof}
  See \autocite{univalent-categories}, Lemma 6.8.
\end{proof}

>>>>

\begin{lemma}
  For every category $ C $, there exists a univalent category $ D $ with a weak equivalence
  \[ \iota: C \hookrightarrow D. \]
\end{lemma}
\begin{proof}
  One construction takes $ D $ to be the full subcategory of the presheaf category $ PC $ of objects that are isomorphic (there \textit{merely exists} an isomorphism) to the Yoneda embedding $ \yo(X) $ of some object $ X : C $ \autocite[][Theorem 8.5]{univalent-categories}.
\end{proof}
We call such a univalent category a \iindex{Rezk completion} of $ C $. Actually, we can call it \textit{the} Rezk completion:
\begin{lemma}[\coqident{Bicategories.RezkCompletions.Uniqueness}{rezk_completion_unique}]
  A Rezk completion is unique.
\end{lemma}
\begin{proof}
  Precomposition with the weak equivalence $ \iota: C \hookrightarrow D $ gives an adjoint equivalence on the functor categories $ [D, E] \simeq [C, E] $ for any univalent category $ E $. From this, it follows that $ \iota $ is the ``initial functor'' from $ C $: any functor from $ C $ to a univalent category factors uniquely through $ \iota $.

@@

Lastly, a result about univalent categories that we will use a couple of times in this thesis:
\begin{lemma}\label{lem:univalen-category-equivalence}
  For a functor between univalent categories $ F: A \to B $, the types `$ F $ is an adjoint equivalence' and `$ F $ is a weak equivalence' are equivalent propositions (see Section \ref{sec:homotopy-props-sets}).
\end{lemma}
\begin{proof}
  See \autocite[][Lemma 6.8]{univalent-categories}.
\end{proof}
